---
title: "Estimating Maximum Growth Rates from Genomic Data with Phydon"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Estimating Maximum Growth Rates from Genomic Data with Phydon}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Introduction

Phydon is a R package that estimates the maximum growth rate of a microbial community from genomic data. The package is based on the method described in [Our paper](). The method takes advantage of phylogenetic signal to improve accuracy of estimation of the maximum growth rate. 

# Installation

You can install the development version of Phydon from GitHub with:

```{r, eval = FALSE}
# install.packages("devtools")
devtools::install_github("xl0418/Phydon")
```


# Usage

First, load the package and the example data.

```{r setup, warning=FALSE}
library(Phydon)
# load the example data
# devtools::load_all()
data_info <- read.csv(system.file("extdata", "data_info.csv", package = "Phydon"))
```

The data_info is a data frame that contains the following columns:

```{r data_info1, echo=FALSE}
data_info
```

The columns are:

- `gene_loc`: the location of the gene file (.ffn) in the package

- `accession_no`: the accession number of the genome


```{r data_info2, echo=FALSE}

# process the directory of the genomic data
genomes <- data_info$accession_no
gene_loc <- c()
for (i in 1:length(genomes)) {
  gene_loc[i] <- system.file("extdata", paste0("genefiles/",genomes[i],"/",genomes[i],".ffn"), package = "Phydon")
}

data_info$gene_loc <- gene_loc
```


Now, you are ready to estimate the maximum growth rate.

```{r, warning=FALSE}
# estimate the maximum growth rate
result <- Phydon(data_info)
```

```{r result, echo=FALSE}
result
```
